The hydra and the rooster

### 2020-07-04 latex/chapter-skippable.tex
Compatibility with Datatypes.CompareSpec

Without ambiguity we will denote the segment $\mathbb{O}_\alpha$ by just $\alpha$.

@@

\begin{itemize}
\item $i\;(i\in\mathbb{N})$ \coq's type \verb@{j:nat | j < i}@ (see also
\href{https://www.math.nagoya-u.ac.jp/~garrigue/lecture/2018_AW/mathcomp-1.7.0/htmldoc/mathcomp.ssreflect.fintype.html#Ordinal}{finite ordinals in Mathcomp}).
\item $\omega$: \coq's type \texttt{nat}, with the order \texttt{Nat.lt}.
\item $\omega^n$ (for some  integer  $n\geq 2$) : the type of $n$-uples of natural numbers, with the lexicographic product of $n$ copies of \texttt{Nat.lt}.
\item  $\omega^\omega$: the set of nonincreasing sequences of natural numbers, lexicographically ordered (also the set of finite multisets of natural numbers).
\item $\epsilon_0$: The set of terms in Cantor normal form (see Chap.~\ref{chap/T1}).
\item $\Gamma_0$: The set of terms in Veblen normal form.
\end{itemize}

>>>>

Without ambiguity we will often denote the segment $\mathbb{O}_\alpha$ by just $\alpha$.

@@

\begin{todo}
Comments on \texttt{cast, compare, bigO}

Show that there is no interesting arihmetic, due to the lack of total succesor, addition, etc.
\end{todo}
\begin{itemize}
\item $i\;(i\in\mathbb{N})$ \coq's type \verb@{j:nat | j < i}@ (see also
\href{https://www.math.nagoya-u.ac.jp/~garrigue/lecture/2018_AW/mathcomp-1.7.0/htmldoc/mathcomp.ssreflect.fintype.html#Ordinal}{finite ordinals in Mathcomp}).
\item $\omega$: \coq's type \texttt{nat}, with the order \texttt{Nat.lt}.
\item $\omega^n$ (for some  integer  $n\geq 2$) : the type of $n$-uples of natural numbers, with the lexicographic product of $n$ copies of \texttt{Nat.lt}.
\item  $\omega^\omega$: the set of nonincreasing sequences of natural numbers, lexicographically ordered (also the set of finite multisets of natural numbers).
\item $\epsilon_0$: The set of terms in Cantor normal form (see Chap.~\ref{chap/T1}).
\item $\Gamma_0$: The set of terms in Veblen normal form.
\end{itemize}
